Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
pass on 4.0 (needs work)

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a givem
source. Column ``pass-in-par.''  shows the number of test cases that
pass in their parent engine. We discarded tests that fail in their
parent engine as we could not reliably indicate the reason for the
failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey. Column ``type-in-all'' shows the number of test
cases whose executions do not throw dynamic type errors in any of the
engines because of an undefined variable or property.  These cases
were captured by looking for the presence of \CodeIn{ReferenceError}
and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object).

We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. Similarly, the \chakra project does not use
  the default well-known assertions available in JS, which the other
  JS engines use.  Instead, it uses its own testing framework,
  WScript. In this case, we could not easily reproduce the \chakra
  unit tests in the other engines since it would raise a
  \texttt{ReferenceError}. Also, updating the other engines to use
  WScript would require a non-trivial manual effort. This is why
  \chakra does not appear in Table~\ref{tab:test-suites}.
  Moreover, we also did not include \hermes in the table because,
  as the reader shall see in Table~\ref{tab:test262}, \hermes presents
  a very low adherence to the Test262 conformance stuite. If we decided
  to keep \hermes, considering only the number of passing tests
  (the ``no-fail-in-all'' column), it would significantly reduce our
  amount of test files.

\Mar{Numbers seem inconsistent. I will stop here...}
For the evaluation of test transplantation, we used
the \totalTestFilesForTestTransplantation{} tests included in the
dashed rectangle under column ``type-in-all'', \ie{}, all tests under
that column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these test and are encouraged to run them. Finally, column
``no-fail-in-all'' shows the tests for which all engines pass. Note
that the set of tests in this column is a subset of the
``type-in-all'' test set. This test set is used in the evaluation of
differential testing as fuzzing seeds. The guarantee that they pass in
all engines assures that, if discrepancies occur, they are related to
the changes in the input as opposed to the original cause of failure.

@@

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, many tests we found
required a Node.js runtime~\cite{node} for execution. Also, as aforementioned,
we did not consider tests from the \chakra{} repository because they depend on
non-portable objects.
Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
worth mentioning that some engines use a custom shell to run tests,
including a harness with specific assertions.  For that, we needed to
make minor changes in the testing infrastructure to be able to run the
tests uniformly across all engines.

More precisely, we needed to mock
non-portable harness functions, which are only available in certain
engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to
make the test file work in the other engine.
For instance, if a test had a statement such as \texttt{print(1==1);}
we manually refactored that statement to \texttt{assertEquals(1,1)}.
If the change would require more substantial manual work, we opted to
discard the test instead. Overall we may have manually refactored more
than a thousand test files.

>>>>

Table~\ref{tab:test-suites} shows the breakdown of tests. Column
``Name'' and ``Source'' show the origin of the test suite. Column
``total'' shows the number of test cases associated with a given
source of \js\ files. Column ``pass-in-par.''  shows the number of
test cases that pass in the corresponding engine. We discarded tests
that fail in their engine as we could not reliably indicate the reason
for the failure, so we assumed the test could be broken. We removed
\testsThatFail{} test cases that fail for that
reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
tests from \smonkey.

Column ``type-in-all'' shows the number of test cases whose executions
do not throw dynamic type errors in any of the engines because of an
undefined variable or property.  These cases were captured by looking
for the presence of \CodeIn{ReferenceError} and \CodeIn{TypeError} on
the output. A \CodeIn{ReferenceError} (respectively,
\CodeIn{TypeError}) is raised when test execution attempts to access
an undefined variable (respectively, property of an object). We
discarded those tests to avoid noise in the experiments as they
indicate some missing feature in the implementation of the engine as
opposed to bugs. For example, some tests use non-portable names
(\eg{}, \jsc's \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. Similarly, the \chakra
project does not use common assertions available used in JS program,
which other JS engines support. Instead, it uses its own testing
framework, WScript. In such cases, we are unable to reproduce the
\chakra unit tests in other engines---it raises a
\CodeIn{ReferenceError}. Also, updating the other engines to use
WScript would require a non-trivial manual effort. This is why \chakra
does not appear in Table~\ref{tab:test-suites}. For the evaluation of
test transplantation, we used the
\totalTestFilesForTestTransplantation{} tests included in the dashed
rectangle under column ``type-in-all'', \ie{}, all tests under that
column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these tests and are encouraged to run them.

Column ``no-fail-in-all'' shows the tests for which all engines
pass. The set of tests in this column is a subset of the
``type-in-all'' test set. The tests in this set are as fuzzing seeds
in the evaluation of differential testing. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure. It is worth noting that we also did not include the tests
from \hermes\ in the table because, as the reader shall see in
Table~\ref{tab:test262}, \hermes presents a very low adherence to the
Test262 conformance suite. If we decided to keep \hermes, considering
only the number of passing tests in all engines (the
``no-fail-in-all'' column), it would significantly \Mar{Not sure if I
  understood the conclusion. Do you mean the total amount of test
  (also from other suites)? Why?}reduce our amount of test files.

@@

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
  the reason?  Please, confirm$\rightarrow$} require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due\Mar{@Gustavo/@Breno, we can mention in the
  author response that we did sanity/diligence check.}.

\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
engines use a custom shell to run tests, including a harness with
specific assertions\Mar{@Igor, can you name which?}. For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine.\Mar{This seems a different problem
  (tests without assertions). I did not understand how this is related
  to portability?}  For instance, if a test had a statement such as
\texttt{print(1==1);} we manually refactored that statement to
\texttt{assertEquals(1,1)}.  If the change would require more
substantial manual work, we opted to discard the test instead. Overall
we may have manually refactored more than a thousand test files.
